Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-14 manuscript/manuscript.tex
fixed mistake in last commit and added the emma-project url (addresses #171) [ci skip]

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials (notebooks~00 and~01).

@@

The present tutorial presents the basics of modern Markov state modeling with PyEMMA. 
However, recent years have seen many extensions of the methodology---many of which are available within PyEMMA. 
We encourage interested readers to look into these methods in the software documentation and to make use of the specific Jupyter notebooks distributed with PyEMMA.

>>>>

Additional technical challenges for large systems include high demands on memory and computation time;
we explain how to deal with those in the tutorials (notebook~01).

@@

The present tutorial presents the basics of modern Markov state modeling with PyEMMA. 
However, recent years have seen many extensions of the methodology---many of which are available within PyEMMA. 
We encourage interested readers to look into these methods in the software documentation
and to make use of the specific Jupyter notebooks distributed with PyEMMA (\url{http://emma-project.org}).
